Case Study: RNA-Seq Differential Analysis (basal ganglia)

### 2018-03-16 datasets/RNA-Seq/RNA-Seq.Rmd
Download only the relevant subset of GTEx.

```{r, dsd-download}
if (!file.exists(count_file)) {
    source("downloadAndSubset.R")
}
dsd <- readRDS(count_file)
```

>>>>

```{r, dsd-download}
if (!file.exists(count_file)) {
    download.file("https://www.dropbox.com/s/pptxqnpsmdkyhcf/brain-counts.rds?dl=1", destfile=count_file)
}
dsd <- readRDS(count_file)
```
